Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

Some journal names were entered in the extraction form with incorrect formatting. Correct this below before running the test.

@@

## Identify sample for journals

@@

# Resolve coding disagreements in articles data

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
d_articles %>%
  filter(exclusion_primary == exclusion_secondary, 
         exclusion_reason_primary != exclusion_reason_secondary) %>%
  select(article_id, sampleID, exclusion_reason_primary, exclusion_reason_secondary)
```
We will resolve these by applying the exclusion criteria hierarchically. In other words, we use the highest level of exclusion criteria assigned by one of the two coders.
1. Access
2. English
3. Retracted 
4. Non-empirical

@@

# Journals data — add JIF and COPE

There is some information about the sample that isn't included in the extracted data files (e.g., JIFs, Web of Science subject category), so we need to load some of that information from the original sample files.

# list of all random journals (some not in sample)
journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
```

For the random journals we can find the JIFs in the prominent journal sample. Some journals do not have a JIF because they haven't been indexed long enough. We manually checked all of these journals. One JIF needed to be added manually for the journal "Journal of Psychology and Theology". The 2021 JIF for this journal is .80.

```{r}
d_journals_prominent <- d_journals %>%
  filter(sampleID %in% c('prominent', 'both'))

journal_list_prominent_all <- journal_list_prominent_all %>% 
  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category)

d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal')

journal_list_random_all <- journal_list_random_all %>%
  select(journal = Journal, WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal')

journal_list_prominent_all <- journal_list_prominent_all %>%
  select(-WOS_first_psych_category)

d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal')

tmp <- d_journals_random %>% filter(is.na(`2021 JIF`)) %>% distinct(journal, .keep_all = T)
write_csv(tmp,here('data', 'prepareSample', 'journals', '02 - modified', 'we_need_jifs.csv'))
```

>>>>

Some journal names were entered in the extraction form with incorrect formatting. Correct this below.

@@

There is some information about the sample that isn't included in the extracted data files (sampleID, JIFs, Web of Science subject category, COPE status), so we need to load some of that information from the original sample files and attached it to the extracted data

# list of all random journals (some not in sample)
journal_list_random_all <- read_csv(here('data','prepareSample','journals', '03 - final', 'journals-random.csv'), show_col_types = F)
```
## Identify sample for journals

@@

For the random journals we can find the JIFs in the prominent journal sample. Some journals do not have a JIF because they haven't been indexed long enough. We manually checked all of these journals on Journal Citation Reports to see if they had been assigned JIFs. One JIF needs to be added manually for the journal "Journal of Psychology and Theology". The 2021 JIF for this journal is .80.

```{r}
# first split d_journals into two data frames based on sample ID
d_journals_prominent <- d_journals %>%
  filter(sampleID %in% c('prominent', 'both'))

# get JIF and WOS subject category for prominent journals
journal_list_prominent_all <- journal_list_prominent_all %>%
  select(journal = `Journal name`, `2021 JIF`, WOS_first_psych_category) # identify the columns we need from the sample data

d_journals_prominent <- left_join(d_journals_prominent, journal_list_prominent_all, by = 'journal') # attach info to extracted data

# get WOS subject category for random journals
journal_list_random_all <- journal_list_random_all %>%
  select(journal = Journal, WOS_first_psych_category) # identify the columns we need from the sample data

d_journals_random <- left_join(d_journals_random, journal_list_random_all, by = 'journal') # attach info to extracted data

# get JIFs for randomly selected journals by extracting them from the list of prominent journals (in the original download, not the sample)
journal_list_prominent_all <- journal_list_prominent_all %>%
  select(-WOS_first_psych_category) # we don't this column

d_journals_random <- left_join(d_journals_random, journal_list_prominent_all, by = 'journal') # attach info to extracted data

d_journals_random <- d_journals_random %>%
  mutate(`2021 JIF` = ifelse(
    journal == "JOURNAL OF PSYCHOLOGY AND THEOLOGY", # for one journal,
    .80, # manually add its JIF
    `2021 JIF`)) # otherwise keep whatever is already in the JIF column

# reunite d_journals_random and d_journals_prominent
d_journals <- bind_rows(
  d_journals_random %>% mutate(sampleID = "random"),
  d_journals_prominent %>% mutate(sampleID = "prominent")
)
rm(d_journals_random)
rm(d_journals_prominent)
```

# Articles data — Resolve coding disagreements

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
d_articles %>%
  filter(exclusion_primary == exclusion_secondary, 
         exclusion_reason_primary != exclusion_reason_secondary) %>%
  select(article_id, sampleID, exclusion_reason_primary, exclusion_reason_secondary)
```

We will resolve these by applying the exclusion criteria hierarchically. In other words, we use the highest level of exclusion criteria assigned by one of the two coders.
1. Access
2. English
3. Retracted 
4. Non-empirical

@@
